Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-16 Tex/elsevier/reply Solar Energy JULY 2019.tex
revised comment (5)
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{resposta} 
We appreciate these comments; we actually realized that our manuscript was unclear. We should highlight that our main research focus is on the validation process of the stand-alone solar PV system instead of the mathematical modelling, which was already investigated in prior studies over the last two decades. Moreover, we compare the results of using automated verification with simulation; real PV systems were employed just to validate the results presented by both approaches (model checking and simulation). Note that the automated verification and simulation tools are intended to be used during the design of the PV system, i.e., before actually buying or deploying the equipment. This information was carefully included in the revised abstract, introduction and conclusion sections since we concluded that it was unclear in the previous version of our manuscript.

The authors hold real load curve and information collected from monitoring system using Raspberri Pi deployed  \textcolor{red}{at House 1, House 2, House 3 and House 4}; however, based on the fact that the automated verification is mathematical and not visual,  \textcolor{red}{(automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS analysis of coded system, with the counterexample detailing the status of the variables that cause a FAIL in the analysis), so it seems that this comparison is not adequate}.

The information from temperature and solar irradiance from every house location, used by the simulation and formal verification tools, come from historical data collected from real stations, which are available in Weather Base and Energy Plus web sites, \textcolor{red}{as presented at Section "References"}. Considering that the idea of our study is to show the effectiveness of the proposed verification method just after the design phase (i.e., before deployment), we believe that it is a plausible procedure \textcolor{red}{and not using weather base stations in each place. Even because the fact that House 1, House 2, House 3, and House 4 (the ones in a riverside indigenous community) do not have weather station available to collect data and the information must be approximated to Manaus data (the closest municipality with historical data and regular measurement of data). Because of that, we decide to include this issue at the Section "5.4 Threats to Validity". We thank you for that specifically comment}.
\end{resposta}

>>>>

\begin{resposta} 
We appreciate these comments; we actually realized that the contributions of our manuscript were unclear. We should highlight that our main research focus is on the validation process of the stand-alone solar PV system instead of the mathematical modelling, which was already investigated in prior studies over the last two decades. Moreover, we compare the results of using automated verification with simulation; real PV systems were employed just to validate the results presented by both approaches (model checking and simulation). Note that the automated verification and simulation tools are intended to be used during the design of the PV system, i.e., before actually buying or deploying the equipment. This information was carefully included in the revised abstract, introduction, and conclusion sections since it was unclear in the previous version of our manuscript.

The authors hold real load curve and information collected from monitoring system using Raspberri Pi deployed in House 1, House 2, House 3 and House 4; however, based on the fact that the automated verification is mathematical and not visual (i.e., automated verifiers do not present curves or plots; they present the result of FAIL or SUCCESS, with a counterexample detailing the status of the variables that cause a FAIL result), we understand that this comparison is not appropriate.

The information from temperature and solar irradiance from every house location, used by the simulation and formal verification tools, come from historical data collected from real stations, which are available in Weather Base and Energy Plus web sites, as presented in our "References" section \textcolor{red}{could you please indicate the references here? for example, [3, 7, 10]}. Considering that the idea of our study is to show the effectiveness of the proposed verification method just after the design phase (i.e., before deployment), we believe that it is a plausible procedure for not using weather base stations in each place since House 1, House 2, House 3, and House 4 (the ones in a riverside indigenous community) do not have weather station available to collect data and the information must be approximated to Manaus data (the closest municipality with historical data and regular measurement of data). Because of that, we decided to add this discussion in Section ``5.4 Threats to Validity''. We thank you for that specific comment.
\end{resposta}
